On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-01-14 paper_lap/manuscript.tex
some edits

Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then

@@

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
Assume that the discretization satisfies the following assumptions:
\begin{enumerate}
\item All panels which are not at a corner, are separated from the closest corner by their panel length.
\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse corresponding to panel $\Gamma_{i}$, and let $\rho_{i}$ 
be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
denotes the length of the panel at the corner.
\end{enumerate}
Under these assumptions, it can be shown that the accuracy in computing the
Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem, is related to the accuracy 
of a Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.
\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{media/geom-restriction-illus}
\caption{Illustrative figure for demonstrating constraints required on the geometry discretization. The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$. Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$. }
\label{fig:illus-cons}
\end{center}
\end{figure}

@@

Using~\cref{lem_adjm}, the above statement implies that the error in computing the $n$ Legendre coefficient of
the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
data given by a Legendre polynomial on the same panel.  %This seems problematic since the right hand side
%is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
%to the double layer potential is identically zero on line segments.

Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.
Recall that $\sigma_{f}$ denote the solution to the Dirichlet problem with boundary data $f$, i.e., 
$\sigma_{f}$ satisfies
\begin{equation}
-\frac{\sigma_{f}(s)}{2}   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
\end{equation}
 Then $\sigma_{f} = -2f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
 \begin{equation}
-\frac{\tilde{\sigma}}{2}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
 \end{equation}
i.e, $\tilde{\sigma}$ is the solution of Dirichle with data at $\tilde{f}$ given by
\begin{equation}
\tilde{f}(s) = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
\end{equation}
Now there are two concerns that need to be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
for any point $s \in [0,L]$ using an $M$ point Gauss-Legendre quadrature on $[s_{1},s_{2}]$, and secondly, 
the resolution of the function $\tilde{f}(s)$ on the given discretization of the boundary.

For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane (since it is a Legendre polynomial)
and the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is corresponding to $\gamma(s)$.
From assumption 2, it follows that
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
the constant $C$ is related to the boundedness of the function $k(s,t)$ when $t$ is complexified.
(Note the error is not $\rho_{0}^{-2M}$ since $P_{M}$ would grow like $\rho_{0}^{M}$ on the $\rho_{0}-$ Bernstein ellipse.) 
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.

>>>>

%Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then

@@

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
Assume that the discretization satisfies the following assumptions:
\begin{enumerate}
\item All panels which are not at a corner, are separated from the closest corner by at least their panel length.
\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse (see \cite{tref_approx}) corresponding to the panel $\Gamma_{i}$, and let $\rho_{i}$ 
be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
denotes the length of the panel at the corner.
\end{enumerate}
Under these assumptions, it can be shown that the accuracy of computing the
Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem using the adjoint discretization is related to the accuracy 
in the computation of the solution to an associated Dirichlet problem.
\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{media/geom-restriction-illus}
\caption{Illustrative figure for demonstrating constraints required on the geometry discretization. The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$. Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$. }
\label{fig:illus-cons}
\end{center}
\end{figure}

@@

Using~\cref{lem_adjm}, the above statement implies that the error in computing the $M$ Legendre coefficients of
the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
data given by a Legendre polynomial on the same panel.

Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.
Recall that $\sigma_{f}$ denotes the solution of the Dirichlet problem with boundary data $f$, i.e., 
$\sigma_{f}$ satisfies
\begin{equation}
-\frac{\sigma_{f}(s)}{2}   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
\end{equation}
 Then $\sigma_{f} = -2f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
 \begin{equation}
-\frac{\tilde{\sigma}}{2}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
 \end{equation}
i.e, $\tilde{\sigma}$ is the solution of the Dirichlet with data $\tilde{f}$ given by
\begin{equation}
\tilde{f}(s) = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
\end{equation}
There are two concerns which must be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
for any point $s \in [0,L]$ using an $M$ point Gauss-Legendre quadrature on $[s_{1},s_{2}]$, and secondly, 
the resolution of the function $\tilde{f}(s)$ on the given discretization of the boundary.

For any $s$ which is contained on the same segment as $\gamma_{[s_{1},s_{2}]}$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane, since it is a Legendre polynomial.
Moreover, the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is at $\gamma(s)$.
From assumption 2, it follows that
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
the constant $C$ is related to the smoothness of $k(s,t)$ as a function of $t \in \mathbb{C}.$
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.
